### 2017-09-26 Sections/physical_architectures_for_quantum_computing.tex
snowflake
minor

@@

\subsection{Continuous variables (CV)} \label{sec:CV_QC} \index{Continuous variable (CV) quantum computation}

>>>>

\begin{figure}
\includegraphics[width=0.9\columnwidth]{snowflake_graph}
\caption{Micro-cluster state comprising a regular tree sturcture, with branching parameter \mbox{$b=4$} and depth \mbox{$d=4$}.} \label{fig:snowflake_graph}
\end{figure}

\comment{Figure: pruning trees}

@@

\subsection{Continuous variables (CV)} \label{sec:CV_QC} \index{Continuous variable quantum computation}

### 2017-09-26 Sections/quantum_repeater_networks.tex
minor

\textit{Quantum repeaters} are devices that allow entanglement to be shared between distant nodes, when no direct line of communication is available from a server to its two clients. This is achieved using a bootstrapped entanglement swapping protocol (Sec.~\ref{sec:swapping}). Most commonly, this entanglement is in the form of Bell-pairs, which, as discussed previously in Sec.~\ref{sec:ent_ultimate}, form a ubiquitous resource for many essential quantum protocols. The actual physical encoding of the entangled states may vary, but is most commonly in the form of polarisation-encoded single-photons or CV states.

>>>>

\textit{Quantum repeaters} are devices that allow high-quality entanglement to be shared between distant nodes, when no direct line of communication is available from a server to its two clients. For example, a satellite in low Earth orbit (Sec.~\ref{sec:quant_space_race}) may be outside simultaneous line-of-sight\index{Line-of-sight} to two distinct ground stations\index{Ground stations}, owing simply to the Earth's curvature\index{Earth curvature}. This is achieved using a bootstrapped entanglement swapping and purification protocol (Secs.~\ref{sec:swapping} \& \ref{sec:ent_purif}). Most commonly, this entanglement is in the form of Bell-pairs\index{EPR pairs}, which, as discussed previously in Sec.~\ref{sec:ent_ultimate}, form a ubiquitous resource for many essential quantum protocols. The actual physical encoding of the entangled states may vary, but is most commonly and archetypically in the form of polarisation-encoded\index{Polarisation encoding} single-photons or CV states\index{Continuous-variable states}.
